---
title: "Gapminder Analysis"
author: "Marieke Jones"
date: "3/11/2019"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
    keep_md: yes
---

# Introduction

Here is my first document

# Let's embed some R code

We'll write an R chunk that loads the tidyverse library and then reads in the GapMinder dataset from the Data subdirectory

```{r}
library(tidyverse)
gm <- read_csv("Data/gapminder.csv")
```

# Investigate gm

Let's look at the gm dataset
```{r}
head(gm)
```

# Our first plot

Showing gdp per capita on the x axis and life expectancy on the y

```{r, fig.cap='Life Exp vs GDP'}
ggplot(gm, aes(gdpPercap, lifeExp)) + geom_point()
```

# A better plot

Adding color by continent and a log scaled x axis

```{r, fig.cap='Life Exp vs GDP'}
ggplot(gm, aes(gdpPercap, lifeExp)) +
  scale_x_log10() +
  geom_point(aes(col=continent))
```


# Trying out a table using kable
See some data using head

```{r}
head(gm)
```

head as a table
```{r, echo = FALSE, results="as.is"}
library(knitr)
kable(head(gm))
```

